How to fix IR

### 2017-08-27 political-analysis-draft/draftPA.tex
code stuff, remake mult eff plots

\begin{table}[ht]
\centering
	\begin{tabular}{r p{4cm} l}
	\hline
		& Central Finding & Does it Replicate in a Network Model? \\ 
		\hline
		Weeks (2012) & Bosses, Juntas and Strongmen are more Aggressive, Machines are Not & Fails to Replicate \\
		Reiter \& Stam (2003) & Personalist Regimes Attack Democracies, Not Vice Versa & Replicates \\ 
		Rose (2004) & WTO Membership Does not Effect Trade & Replicates \\ 
		McDonald (2004) & Lower Trade Barriers and Higher Trade Lead to Peace & Fails to Replicate \\ 
		% Gibler (2017) & Power Parity at time of Entry to International System Inceases Conflict & Fails to Replicate \\ 
	\hline
	\end{tabular}
\end{table}

\begin{table}[ht]
\centering
\begin{tabular}{ll cc}
~ & ~ & GLM & AME \\
\multirow{2}{*}{Weeks (2012)} & AUC (ROC) & 0.64 & 0.97 \\
~ & AUC (PR) & 0.004 & 0.15 \\
\multirow{2}{*}{Reiter \& Stam (2003)} & AUC (ROC) & 0.92 & 0.96 \\
~ & AUC (PR) & 0.08 & 0.15 \\
\multirow{2}{*}{Rose (2004)} & RMSE & 3.23 & 1.99 \\
~ & RM-D-SE & 2.01 & 1.06 \\
\multirow{2}{*}{McDonald (2004)} & AUC (ROC) & 0.92 & 0.99 \\
~ & AUC (PR) & 0.13 & 0.28 \\
% \multirow{2}{*}{Gibler (2017)} & AUC (ROC) & 0.92 & 0.96 \\
% ~ & AUC (PR) & 0.08 & 0.15 \\
\end{tabular}
\end{table}

>>>>

\begin{table}[ht]
\centering
	\begin{tabular}{l| p{7cm} l}
		& \multirow{2}{*}{Central Finding} & Does it Replicate \\ 
		& &  in a Network Model? \\
		\hline\hline
		Weeks (2012) & Bosses, Juntas and Strongmen are more Aggressive, Machines are Not & Fails to Replicate \\
		\hline
		Reiter \& Stam (2003) & Personalist Regimes Attack Democracies, Not Vice Versa & Replicates \\ 
		\hline
		Rose (2004) & WTO Membership Does not Effect Trade & Replicates \\ 
		\hline
		McDonald (2004) & Lower Trade Barriers and Higher Trade Lead to Peace & Fails to Replicate \\ 
		\hline
		Gibler (2017) & Power Parity at time of Entry to International System Inceases Conflict & Fails to Replicate \\ 
	\hline\hline
	\end{tabular}
\end{table}

\begin{table}[ht]
\centering
\begin{tabular}{l|l cc}
~ & ~ & GLM & AME \\
\hline\hline
\multirow{2}{*}{Weeks (2012)} & Area Under ROC Curve (AUC-ROC) & 0.64 & 0.97 \\
~ & Area Under PR Curve (AUC-PR) & 0.004 & 0.15 \\
\hline
\multirow{2}{*}{Reiter \& Stam (2003)} & AUC (ROC) & 0.92 & 0.96 \\
~ & AUC (PR) & 0.08 & 0.15 \\
\hline
\multirow{2}{*}{McDonald (2004)} & AUC (ROC) & 0.92 & 0.99 \\
~ & AUC (PR) & 0.13 & 0.28 \\
\hline
\multirow{2}{*}{Gibler (2017)} & AUC (ROC) & 0.52 & xx \\
~ & AUC (PR) & 0.004 & xx \\
\hline
\multirow{2}{*}{Rose (2004)} & Root Mean Squared Error (RMSE) & 3.23 & 1.99 \\
~ & Root Median Squared Error (RMDSE) & 2.01 & 1.06 \\
\hline\hline
\end{tabular}
\end{table}
